The Concurrent Calculi Formalisation Benchmark

### 2024-02-19 short-paper/short-paper.tex
Small edits to introduction for brevity and clarity.

The POPLMark challenge~\cite{POPLMark}
played a pivotal role in advancing the field of proof assistants,
libraries, and best practices for programming language
mechanisation. By providing a shared framework for systematically
evaluating mechanisation techniques, it catalysed a significant
shift towards publications that include mechanised proofs within the programming language research community.

POPLMark Reloaded~\cite{POPLMarkReloaded} introduced a program akin to
the original POPLMark challenge, specifically targeting proofs related
to logical relations. While these initiatives had a narrow focus,
their authors recognized the importance of addressing broader topics
in the future, including coinduction and linearity.

In this spirit, we introduce a new collection of benchmark problems
specifically crafted to tackle common challenges encountered during
the mechanisation of formal models for concurrent and distributed
programming languages. Our focus extends particularly to process
calculi.
Concurrent calculi are notably subtle: For instance, it took nine
years before the incorrect proof of type safety in the seminal paper
by Honda et al.~\cite{Honda1998} was rectified in Yoshida \&
Vasconcelos’s subsequent work\cite{Yoshida2007}.
Similarly, many
key results in papers on session types have turned out
to be false later on~\cite{Gay2020,10.1145/3290343}, illustrating the
value of machine-checkable proofs.

@@

We have begun collecting solutions to our challenges on our website:
%
\begin{center}
  \url{https://concurrentbenchmark.github.io/}
\end{center}
%
In the longer term, we expect to use the website for promoting best
practices, tutorials and guidelines derived from solutions to our
challenges.  We encourage anyone interested to try the challenges
using their favourite tools and techniques, and to send us their
solutions.

>>>>

The POPLMark challenge~\cite{POPLMark}
played a pivotal role in advancing the field of proof assistants,
libraries, and best practices for programming language
mechanisation. By providing a shared framework for systematically
evaluating mechanisation techniques, it catalysed a significant
shift towards publications that include mechanised proofs within the programming language research community.
POPLMark Reloaded~\cite{POPLMarkReloaded} introduced a similar programme targeting proofs using logical relations.
These initiatives had a narrow focus, but their authors recognised the importance of addressing topics such as coinduction and linearity in the future.

In this spirit, we introduce a new collection of benchmark problems
specifically crafted to tackle common challenges encountered during
the mechanisation of formal models for concurrent and distributed
programming languages.
We particularly focus on process calculi.
Concurrent calculi are notably subtle: For instance, it took nine
years before the incorrect proof of type safety in the seminal paper
by Honda et al.~\cite{Honda1998} was rectified in Yoshida \&
Vasconcelos’s subsequent work\cite{Yoshida2007}.
Similarly, several key results in papers on session types have turned out
to be false later on, illustrating the
value of machine-checked proofs~\cite{Gay2020,10.1145/3290343}.

@@

We have begun collecting solutions to our challenges on our website:
%
\begin{center}
  \url{https://concurrentbenchmark.github.io/}
\end{center}
%
In the future, we expect to use the website to promote best practices and tutorials derived from solutions to our challenges.
We encourage everyone to try the challenges using their favourite techniques, and to send us their solutions.
